---
title: "PracticeCSUF"
author: "Haley Bjursten"
date: "6/22/2020"
output: html_document
---

---
title: "CSUF practice"
author: "Haley Bjursten"
date: "6/7/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Desktop/R Working Directory")
```


```{r}
#packages I may be using
library(rjson)
library(jsonlite)
library(saotd) #i can't get this one to install on my version of R
library(tidyverse)
library(lubridate)
library(zoo)
library(knitr)
library(utils)
library(rtweet)
library(dplyr) #########this is part of tidyverse so you don't have to call it individually
library(tidyr)
library(tidytext)
library(tidyverse)
#install.packages("twitteR")
library(twitteR)
```

```{r}
#read 1/24 of the super big dataset using read_csv instead of read.csv
#covidtweets <- read_csv("coronavirus-through-09-June-2020-00.csv")
covidtweets <- subset(covidtweets, lang == "en")
TD <- covidtweets %>%
  dplyr::sample_n(size = 100)
```

```{r}
#create random sample of the larger dataset?? this is just what the website had me do 
TD <- covidtweets %>%
  dplyr::sample_n(size = 100)
head(TD)
```


```{r}
TD_Tidy <- saotd::tweet_tidy(DataFrame = TD)
TD_Tidy$Token[3:8]%>%
  knitr::kable("html")
```

```{r}
#twitter info
app_name = 'CSUFSentimentAnalysis'
consumer_key = '4FotHBNuYzgVW9eRjX7VT1gQN'
consumer_secret = 'r8veJvJIUGERrZNOso5V8ivhRADD4niJkev4JyZmAtHu1ybTPD'
access_token = '1260639569629700101-6HuoMzITOpjKvL8TTiLaPLwVhmiSzs'
access_secret = 'OrCT1hOFWHNn8CU76X7hMrA1fHk3TvcBrBH9XoNDS5Wa2'

hashtags <- c("#covid19", "#coronavirus", "#coronaoutbreak")

#THIS PART IS OFF
twitterdata <- file.path(tempdir(), "twitterdata.RData")

tweet_acquire(consumer_key = consumer_key,
              consumer_secret = consumer_secret,
              access_token = access_token, 
              access_secret = access_secret,
              HT = hashtags,
              num_tweets = 1000,
              file_name = twitterdata.RData, #THIS IS WHAT'S CAUSING PROBLEMS
              distinct = TRUE)

load("twitterdata") #WON'T LOAD^^^
```

```{r}
#strip the text
library(tidytext)
TD$stripped_text <- gsub("http\\S+","",TD$text)

TD_stem <- TD %>%
  dplyr::select(stripped_text) %>%
  unnest_tokens(word, stripped_text)

#remove stop words
clean_TD <- TD_stem %>%
  anti_join(stop_words)
```

```{r}
#here is my attempt to start a time series data plan by establishing by date, but having a lot of trouble with making time series
start_date <- as.POSIXct('2020-03-11 00:00:00')
end_date <- as.POSIXct('2020-06-08 00:00:00')
options(stringAsFactors = FALSE)
```

```{r}
#visualizing the unique words
library(tidyverse)
clean_TD %>%
  count(word, sort=TRUE)%>%
  top_n(15)%>%
  mutate(word = reorder(word, n))%>%
  ggplot(aes(x = word, y = n))+
  geom_col()+
  xlab(NULL)+
  coord_flip()+
  labs(x = "Count",
       y = "Unique words",
       title = "Count of unique words found in tweet")
```



```{r}
#top 10 words in #covid19 tweets
cleaned_tweets.covid19 %>%
  count(word, sort=TRUE)%>%
  top_n(10) %>%
  mutate(word = reorder(word,n))%>%
  ggplot(aes(x=word,y=n))+
  geom_col()+
  xlab(NULL)+
  coord_flip()+
  theme_classic()+
  labs(x="count",y="unique words", title = "unique word counts from #covid19 tweets")

#top 10 words in #covid19 tweets
cleaned_tweets.coronavirus %>%
  count(word, sort=TRUE)%>%
  top_n(10) %>%
  mutate(word = reorder(word,n))%>%
  ggplot(aes(x=word,y=n))+
  geom_col()+
  xlab(NULL)+
  coord_flip()+
  theme_classic()+
  labs(x="count",y="unique words", title = "unique word counts from #coronavirus tweets")
```
```{r}
#starting to get sentiment data
library(tidytext)
library(textdata)
get_sentiments("bing") %>%
  filter(sentiment=="positive")
get_sentiments("bing") %>%
  filter(sentiment=="negative")
get_sentiments("afinn") %>%
  filter(value=="3")
get_sentiments("afinn") %>%
  filter(value=="-3")
```

```{r}
#bing sentiment analysis
bing_covid19 = clean_TD %>%
  inner_join(get_sentiments("bing"))%>%
  count(word, sentiment, sort=TRUE)%>%
  ungroup()
bing_covid19 %>%
  group_by(sentiment)%>%
  top_n(10)%>%
  ungroup()%>%
  mutate(word = reorder(word,n))%>%
  ggplot(aes(word,n,fill=sentiment))+
  geom_col(show.legend = FALSE)+
  facet_wrap(~sentiment, scales = "free_y")+
  labs(title = "tweets containing '#covid19', '#coronavirus', '#coronaoutbreak'",
       y = "contribution to sentiment",
       x = NULL)+
  coord_flip()+
  theme_bw()
```

```{r}
#try to visualize using a wordcloud
library("wordcloud")
library("wordcloud2")
library("RColorBrewer")
library("tm")

#this is using the TD dataset, so maybe would want to do it on part of the bigger dataset?
wordcloud_covid19 <- clean_TD$word
#covid19, coronavirus, coronaoutbreak wordcloud
wordcloud(words = wordcloud_covid19, max.words=100,min.freq=1,colors=brewer.pal(8,"Dark2"),random.order = FALSE)
```


```{r}
#looking at unigrams, bygrams, and trigrams of common words from dataset
saotd::unigram(DataFrame = TD)%>%
  dplyr::top_n(10)%>%
  knitr::kable("html", caption = "Twitter data Uni-Grams")

saotd::bigram(DataFrame = TD)%>%
  dplyr::top_n(10)%>%
  knitr::kable("html", caption = "Twitter data Bi-Grams")

saotd::trigram(DataFrame = TD)%>%
  dplyr::top_n(10)%>%
  knitr::kable("html", caption = "Twitter data Tri-Grams")
```

```{r}
#tried merging some terms, but don't think it did much
TD_Merge <- merge_terms(DataFrame = TD, term = "death rate", term_replacement = "death_rate")
TD_Merge <- merge_terms(DataFrame = TD, term = "sporting events", term_replacement = "sporting_events")
TD_Merge <- merge_terms(DataFrame = TD, term = "protective equipment", term_replacement = "protective_equipment")



saotd::unigram(DataFrame = TD_Merge)%>%
  dplyr::top_n(10)%>%
  knitr::kable("html", caption = "Twitter data Uni-Grams")

saotd::bigram(DataFrame = TD_Merge)%>%
  dplyr::top_n(10)%>%
  knitr::kable("html", caption = "Twitter data Bi-Grams")

saotd::trigram(DataFrame = TD_Merge)%>%
  dplyr::top_n(10)%>%
  knitr::kable("html", caption = "Twitter data Tri-Grams")
```
EVERYTHING FROM HERE BELOW will not run...
Something is wrong, but I can't figure out exactly what. I am not sure if it's different maybe because tha hashtags aren't specified? I tried something but it didn't work with the hashtags... here is the website again:https://rdrr.io/cran/saotd/f/vignettes/saotd.Rmd
```{r}
#THIS WHOLE CHUNK DO NOT RUN - SOMETHING WRONG with this code... I don't know what though
TD_Bigram <- saotd::bigram(DataFrame = TD_Merge)
saotd::bigram_network(BiGramDataFrame = TD_Bigram,
                      number = 30,
                      layout = "fr",
                      edge_color = "blue",
                      node_color = "black",
                      node_size = 3,
                      set_seed = 1234)

TD_Corr <- saotd::word_corr(DataFrameTidy = TD_Tidy,
                            number = 100,
                            sort = TRUE)

saotd::word_corr_network(WordCorr = TD_Corr,
                         Correlation = 0.1,
                         layout = "fr",
                         edge_color = "blue",
                         node_color = "black",
                         node_size = 1)
```

```{r}
#https://rdrr.io/cran/saotd/f/vignettes/saotd.Rmd

#undre Explore section, this part also was not working... this would be to get the sentiment
TD_Scores <- saotd::tweet_scores(DataFrameTidy = TD_Tidy,
                                 HT_Topic = hashtags)

saotd::posneg_words(DataFrameTidy = TD_Tidy,
                    num_words = 5)
```

```{r}
saotd::tweet_max_scores(DataFrameTidyScores = TD_Scores,
                        HT_Topic = "hashtag")

saotd::tweet_min_scores(DataFrameTidyScores = TD_Scores,
                        HT_Topic = "hashtag")

saotd::tweet_max_scores(DataFrameTidyScores = TD_Scores,
                        HT_Topic = "hashtag",
                        HT_Topic_Selection = "fake")
```

## TOPIC ANALYSIS

```{r}
saotd::number_topics(DataFrame = TD,
                     num_cores = 2L,
                     min_clusters = 2,
                     max_clusters = 12,
                     skip = 1,
                     set_seed = 1234)
```

```{r}
TD_Topics <- saotd::tweet_topics(DataFrame = TD,
                                 clusters = 5,
                                 method = "Gibbs",
                                 set_seed = 1234,
                                 num_terms = 10)
```

```{r}
TD_Topics <- TD_Topics%>%
  dplyr::mutate(Topic = stringr::str_replace_all(Topic, "^1$", "luggage"))%>%
  dplyr::mutate(Topic = stringr::str_replace_all(Topic, "^2$", "gate_delay"))%>%
  dplyr::mutate(Topic = stringr::str_replace_all(Topic, "^3$", "customer_service"))%>%
  dplyr::mutate(Topic = stringr::str_replace_all(Topic, "^4$", "enjoy"))%>%
  dplyr::mutate(Topic = stringr::str_replace_all(Topic, "^5$", "other_delay"))

```

```{r}
TD_Topics_Tidy <- saotd::tweet_tidy(DataFrame = TD_Topics)
TD_Topics_Scores <- saotd::tweet_scores(DataFrameTidy = TD_Topics_Tidy,
                                        HT_Topic = "topic")
```

```{r}
saotd::tweet_max_scores(DataFrameTidyScores = TD_Topics_Scores,
                        HT_Topic = "topic")

saotd::tweet_min_scores(DataFrameTidyScores = TD_Topics_Scores,
                        HT_Topic = "topic")

saotd::tweet_max_scores(DataFrameTidyScores = TD_Topics_Scores,
                        HT_Topic = "topic",
                        HT_Topic_Selection = "United")
```

## VISUALIZATIONS

```{r}
saotd::tweet_corpus_distribution(DataFrameTidyScores = TD_Scores,
                          color = "black",
                          fill = "white")

saotd::tweet_distribution(DataFrameTidyScores = TD_Scores,
                          binwidth = 1,
                          HT_Topic = "hashtag",
                          color = "black",
                          fill = "white")
```

```{r}
saotd::tweet_box(DataFrameTidyScores = TD_Scores,
                 HT_Topic = "hashtag")

saotd::tweet_violin(DataFrameTidyScores = TD_Scores,
                 HT_Topic = "hashtag")
```

```{r}
saotd::tweet_time(DataFrameTidyScores = TD_Scores,
                  HT_Topic = "hashtag")
```

```{r}
saotd::tweet_distribution(DataFrameTidyScores = TD_Topics_Scores,
                          binwidth = 1,
                          HT_Topic = "topic",
                          color = "black",
                          fill = "white")
```

```{r}
saotd::tweet_box(DataFrameTidyScores = TD_Topics_Scores,
                 HT_Topic = "topic")

saotd::tweet_violin(DataFrameTidyScores = TD_Topics_Scores,
                 HT_Topic = "topic")
```

```{r}
saotd::tweet_time(DataFrameTidyScores = TD_Topics_Scores,
                  HT_Topic = "topic")
```
